\bf Teaching analysis reproducibility with accessibility: Enriching secondary documentation to support skill level diversity of users.

### 2022-02-11 jsdse/Manuscript.tex
elaborating on inclusivity

\bigskip
\begin{abstract}
Research reproducibility is essential for scientific development. Yet, rates of reproducibility
are low, especially in the natural sciences. As increasingly more research is relying on
computing tools and software, efforts for improving
reproducibility rates have focused on digital availability of research workflows
as computer code, as well as raw and processed data in computer readable form.
However, making research products digitally available does not
necessarily ensures that
they can be easily reached by the majority of a target user base, let alone the general population,
making them effectively inaccessible, counteracting availability, and hindering reproducibility.

In this paper, we argue that accessibility of research products is a key aspect for
improving reproducibility rates.
While accessibility typically addresses differences in abilities (visual, hearing, cognitive).

across individuals, we particularly address barriers to accessibility at the
technological, social and pedagogical level.

Using an example within evolutionary biology, we identify barriers to
accessibility in the natural sciences:
%% list the barriers
specialized jargon, user programming experience, cognitive load,

@@

      A couple of brand new marshmallow bags remained in a common office area after
      a social gathering.
      The marshmallows were not claimed by anybody, so they were left in the common area,
      freely available to be taken or eaten by anyone in the office.
      Yet, the marshmallow bags stayed in the common area, unopened for days and even weeks.
      It was not until someone decided to open the bags and placed the marshmallows on a tray,
      that people started actually eating them. They were gone in a matter of hours.
      Scientific products are not sweet as marshmallows, but they are a coveted resource.
      While sharing, describing and documenting makes scientific products available,
      it does not necessarily makes them accessible.

      ** Now, explain different types of barriers to accessibility in science
      (Jessica: Maybe say that lack of accessibility can be due to a number of
      factors (physical, resources, economic), but one critical factor is the use
      of impenetrable expert language.)

      For example, documentation of an
      available scientific workflow might be written using expert language that is too foreign
      for a general audience to successfully reproduce the workflow.

      While some individuals might
      be able to invest the time to learn the expert language to successfully reproduce
      the workflow, this will not be the case for the majority; even if it is
      something that would be useful long term, the short term time investment
      is often too high for individuals to engage with it, making the workflow and its results
      effectively inaccessible and hence unavailable to the majority of the community.
    }%
}
\bigskip

>>>>

\bigskip
\begin{abstract}
Research reproducibility is essential for scientific development. Yet, rates of reproducibility
are low, especially in the natural sciences. As increasingly more research is relying on
computing tools and software, efforts for improving
reproducibility rates have focused on digital availability of research workflows
as computer code, as well as raw and processed data in computer readable form.
However, making research products digitally available does not
necessarily ensures that
they can be easily reached by the majority of a target user base, let alone the general population,
making them effectively inaccessible, counteracting availability, and hindering reproducibility.
Thus, accessibility of research products is a key aspect for the long term improvement
of reproducibility rates.
Using an example within evolutionary biology, we identify inclusivity barriers to accessibility,
% accessibility typically refers to addressing differences in abilities (visual, hearing, cognitive).
research products in the natural sciences:
%% list the barriers
use of highly specialized computing jargon and programming techniques; high cognitive load,
unspecified, unclear or lengthy goals; content-focused descriptions instead of user-focused;
inflexible learning environment; unapproachable (cold or intimidating) language;
and little to no diversity of representation of information.

@@

      ** Now, explain different types of barriers to accessibility in science
      (Jessica: Maybe say that lack of accessibility can be due to a number of
      factors (physical, resources, economic), but one critical factor is the use
      of impenetrable expert language.)
    }%
}
\bigskip
